Exploratory analysis of context: Regression Analysis

### 2022-10-07 analysis/exploratory/context_versus_nocontext/rscripts/analysis.Rmd
updated push

@@

## Every paraphrase

@@

## The paraphrase

>>>>

# Wh-word sub-models

## What
```{r}
d_what = d.ms.ma %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

# m.what = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id) + (1+cParaphrase|VerbLemma), data=d_what)

# saveRDS(m.what, "../models/what.rds")

m.what <- readRDS("../models/what.rds")
summary(m.what)

# m.what.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what)
# summary(m.what.simple)
```

## How
```{r}
d_how = d.ms.ma %>% 
  filter(Wh=="how") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.how = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id) + (1+cParaphrase|VerbLemma), data=d_how)

# saveRDS(m.how, "../models/how.rds")

m.how <- readRDS("../models/how.rds")
summary(m.how)

# m.how.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_how) 
# summary(m.how.simple)
```

## Where
```{r where model}
d_where = d.ms.ma %>% 
  filter(Wh=="where") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.where = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id) + (1+cParaphrase|VerbLemma), data=d_where)

saveRDS(m.how, "../models/how.rds")

m.how <- readRDS("../models/how.rds")
summary(m.how)
summary(m.where)

# m.where.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where) 
# summary(m.where.simple)
```

## WHY
```{r why model}
d_why = d.ms.ma %>% 
  filter(Wh=="why") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.why = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id) + (1+cParaphrase|VerbLemma), data=d_why)

saveRDS(m.how, "../models/how.rds")

m.how <- readRDS("../models/how.rds")
summary(m.how)
summary(m.why)

# m.why.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why) 
# summary(m.why.simple)
```

## Who
```{r who model}
d_who = d.ms.ma %>% 
  filter(Wh=="who") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.who = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id) + (1+cParaphrase|VerbLemma), data=d_who)

saveRDS(m.how, "../models/how.rds")

m.how <- readRDS("../models/how.rds")
summary(m.how)
summary(m.who)

# m.who.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id), data=d_who) 
# summary(m.who.simple)
```

## When
```{r when model}
# have to use less random effects structure
d_when = d.ms.ma %>% 
  filter(Wh=="when") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.when = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase|tgrep_id) + (1+cParaphrase|VerbLemma), data=d_when)

saveRDS(m.how, "../models/how.rds")

m.how <- readRDS("../models/how.rds")
summary(m.how)
summary(m.when)

# simple effects
# m.when.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|tgrep_id), data=d_when) 
# summary(m.when.simple)
```

@@

## What
```{r}
d_what = a_data %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.what = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_what)
# saveRDS(m.a.what, "../models/a-what.rds")

m.a.what <- readRDS("../models/a-what.rds")
summary(m.a.what)

# m.what.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what)
# summary(m.what.simple)
```

## How
```{r}
d_how = a_data %>% 
  filter(Wh=="how") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.how = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_how)
# saveRDS(m.a.how, "../models/a-how.rds")

m.a.how <- readRDS("../models/a-how.rds")
summary(m.a.how)

# m.how.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_how) 
# summary(m.how.simple)
```

## Where
```{r where model}
d_where = a_data %>% 
  filter(Wh=="where") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.where = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_where) 
# saveRDS(m.a.where, "../models/a-where.rds")

m.a.where <- readRDS("../models/a-where.rds")
summary(m.a.where)

# m.where.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where) 
# summary(m.where.simple)
```

## WHY
```{r why model}
d_why = a_data %>% 
  filter(Wh=="why") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# table(d_why$workerid,d_why$ModalPresent)

# m.a.why = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_why)
# saveRDS(m.a.why, "../models/a-why.rds")

m.a.why <- readRDS("../models/a-why.rds")
summary(m.a.why)

# m.why.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why) 
# summary(m.why.simple)
```

## Who
```{r who model}
d_who = a_data %>% 
  filter(Wh=="who") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.who = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_who) 
# saveRDS(m.a.who, "../models/a-who.rds")

m.a.who <- readRDS("../models/a-who.rds")
summary(m.a.who)

## When
```{r when model}
# have to use less random effects structure
d_when = a_data %>% 
  filter(Wh=="when") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.when = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_when)

# saveRDS(m.a.when, "../models/a-when.rds")

m.a.when <- readRDS("../models/a-when.rds")
summary(m.a.when)

# simple effects
# m.when.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|tgrep_id), data=d_when) 
# summary(m.when.simple)
```

# Every paraphrase

@@

## What
```{r}
d_what = every_data %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.what = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_what)
# saveRDS(m.every.what, "../models/every-what.rds")

m.every.what <- readRDS("../models/every-what.rds")
summary(m.every.what)

# m.what.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what)
# summary(m.what.simple)
```

## How
```{r}
d_how = every_data %>% 
  filter(Wh=="how") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.how = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_how)
# saveRDS(m.every.how, "../models/every-how.rds")

m.every.how <- readRDS("../models/every-how.rds")
summary(m.every.how)

# m.how.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_how) 
# summary(m.how.simple)
```

## Where
```{r where model}
d_where = every_data %>% 
  filter(Wh=="where") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.where = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_where)
# saveRDS(m.every.where, "../models/every-where.rds")

m.every.where <- readRDS("../models/every-where.rds")
summary(m.every.where)

# m.where.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where) 
# summary(m.where.simple)
```

## WHY
```{r why model}
d_why = every_data %>% 
  filter(Wh=="why") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.why = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_why)
# saveRDS(m.every.why, "../models/every-why.rds")

m.every.why <- readRDS("../models/every-why.rds")
summary(m.every.why)

# m.why.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why) 
# summary(m.why.simple)
```

## Who
```{r who model}
d_who = every_data %>% 
  filter(Wh=="who") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.who = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_who)
# saveRDS(m.every.who, "../models/every-who.rds")

m.every.who <- readRDS("../models/every-who.rds")
summary(m.every.who)

## When
```{r when model}
# have to use less random effects structure
d_when = every_data %>% 
  filter(Wh=="when") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.when = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_when)
# saveRDS(m.every.when, "../models/every-when.rds")

every.when <- readRDS("../models/every-when.rds")
summary(m.every.when)

# simple effects
# m.when.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|tgrep_id), data=d_when) 
# summary(m.when.simple)
```

# The paraphrase
